---
title: "Environment Clearance Odisha"
author: "Anustubh Agnihotri"
date: "`r Sys.Date()`"
output:
  html_document:
    df_print: paged
---

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list=ls())
```


```{r}
library(sf)
library(tidyverse)
library(cowplot)
library(patchwork)
library(lfe)
library(expss)
library(lubridate)
library(zoo)
```

```{r}
#user <- "prana"
user <- "agnihotri"

```

## Analysis Plan 

1. Look at the three datasets for Odisha -  EC Level, Detailed Timeline, and Detailed EC Report 
2. For the Tehsil shp file create an alignment variable 
3. Merge the data with the Tehsil Shp File
4. Do some basic descriptives 


## Odisha Files

```{r}

#Same as Main Data 
ec_odisha <- read.csv(paste0("C:/Users/",user,"/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Orissa_ec_additional_data.csv")) %>% distinct()

ec_odisha_main <- read.csv(paste0("C:/Users/",user,"/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/merged_maindata.csv")) %>% distinct()

#RA downloaded the additional data 
missing_parivesh_main<-read.csv('C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Orissa_ec_maindata_parivesh_missing.csv',stringsAsFactors = F)

ec_odisha_main_missing<-ec_odisha_main%>%
  filter(Proposal%in%missing_parivesh_main$Proposal.No.)

##Create a separate data frame for the missing data
ec_odisha_main_not_missing<-ec_odisha_main%>%
  filter(!Proposal%in%missing_parivesh_main$Proposal.No.)

#Use the form data from parivesh to add Tehsil and District 
missing_parivesh_form_data<-read.csv('C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Orissa_ec_formdata_parivesh_missing.csv',stringsAsFactors = F)

missing_parivesh_form_data<-missing_parivesh_form_data%>%
  select(District.Name,Tehsil.Name,Proposal.No.)

ec_odisha_main_missing$Proposal.No.<-ec_odisha_main_missing$Proposal

ec_odisha_main_missing<-dplyr::left_join(ec_odisha_main_missing,missing_parivesh_form_data,by='Proposal.No.')

ec_odisha_main_missing$District<-ec_odisha_main_missing$District.Name
ec_odisha_main_missing$Tehsil<-ec_odisha_main_missing$Tehsil.Name

ec_odisha_main_missing <- select(ec_odisha_main_missing, -c(District.Name,Tehsil.Name,Proposal.No.))  

#Create a final dataset 
#which will be used by DEOs to add location data manually 
temp<-bind_rows(ec_odisha_main_missing, ec_odisha_main_not_missing)

ec_odisha_main<-temp

write.csv(ec_odisha_main,'C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/merged_maindata_with_parivesh1.csv')
```


```{r read}
#read the file where RA has manually entered Tehsil 

ec_odisha_main<-read.csv('C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/merged_maindata_with_parivesh_ra.csv')

```

#Timeline Has Different components

```{r timeline}
#Timeline data 
ec_detailed_timeline_odisha<-read.csv(paste0("C:/Users/",user,"/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/merged_timelinedata.csv")) %>% distinct()

#Missingnes 
length(which(ec_detailed_timeline_odisha$Accepted.by.SEIAA.and.forwarded.to.SEAC==""))

#Overlapping Proposal Numbers 
table(ec_odisha$Proposal%in%ec_detailed_timeline_odisha$Proposal.Number)

#Parivesh missing data downloaded by RA
missing_parivesh_timeline<-read.csv('C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Orissa_ec_timelinedata_parivesh_missing.csv',stringsAsFactors = F)

ec_odisha_timeline_missing<-ec_detailed_timeline_odisha%>%
  filter(Proposal.Number%in%missing_parivesh_timeline$Proposal.Number)

ec_odisha_main_select<-ec_odisha_main%>%
  select(Proposal,Status)%>%
  ungroup()

table(ec_detailed_timeline_odisha$Proposal.Number%in%ec_odisha_main_select$Proposal)

ec_odisha_main_select<-ec_odisha_main_select%>%
  rename(Proposal.Number=Proposal)

ec_detailed_timeline_odisha<-ec_detailed_timeline_odisha%>%
  ungroup()

ec_detailed_timeline_odisha_status<-inner_join(ec_detailed_timeline_odisha,ec_odisha_main_select,by='Proposal.Number')

write.csv(ec_detailed_timeline_odisha_status,'C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/ec_detailed_timeline_odisha_status.csv')


```


```{r form-2}
ec_form2_odisha <- read.csv(paste0("C:/Users/",user,"/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/merged_form2data.csv")) %>% distinct()

##Missingness in Form2?
length(which(ec_form2_odisha$Name.of.the.Company==""))

#Lot of Missing                                       
table(ec_odisha$Proposal%in%ec_form2_odisha$Proposal.Number)

```


## Types of Projects 

- 60% of the applications were granted EC 

```{r}

ec_odisha_main$Status_Simplified <- ifelse(grepl('EC Granted',ec_odisha_main$Status),'EC Granted',
                                    ifelse(grepl('Delisted',ec_odisha_main$Status),'Delisted',
                                           ifelse(grepl('Rejected',ec_odisha_main$Status),'Rejected',
                                    ifelse(ec_odisha_main$Status=='WithdrawEC','Withdrawn','Other'))))


ec_odisha_main$Category_Simplified <- ifelse(grepl('INFRA',ec_odisha_main$Category),'INFRA',
                                    ifelse(grepl('Industrial',ec_odisha_main$Category),'Industrial',
                                    ifelse(ec_odisha_main$Category=='Non-Coal Mining','Non-Coal Mining','Other')))

```




```{r descriptives}
ec_odisha_main%>%
  group_by(Status_Simplified)%>%
  count()%>%
  arrange(-n)%>%
  ungroup()%>%
  mutate(Percent=round(n*100/sum(n),0))



ec_odisha_main%>%
  group_by(Category_Simplified,Status_Simplified)%>%
  count()%>%
  ungroup()%>%
    group_by(Category_Simplified)%>%
  mutate(Percent=round(n*100/sum(n),0))%>%
  ungroup()

```


## Location of Projects 

- 10% of the applications do not have District/Tehsil 

- Can this be recovered from Form 2?

```{r}
ec_odisha_main%>%
  group_by(District)%>%
  count()%>%
  arrange(-n)%>%
  ungroup()%>%
  mutate(Percent=round(n*100/sum(n),0))
  
```

## Get Dates 


```{r}

#For the projects that were delisted or withdrawn 
#Date 2 is when EC was filed
#Date 1 is actually the date on which TOR was submitted
index_with_tor<-which(grepl('TOR',ec_odisha_main$Date_1))

ec_odisha_main$Date_1[index_with_tor]<-ec_odisha_main$Date_2[index_with_tor]

ec_odisha_main$Date_2[index_with_tor]<-"NA"

#Write Function For Extracting Date 
extract_after_colon <- function(input) {
  split_string <- strsplit(input, ":")
  extracted_text <- sapply(split_string, function(x) trimws(x[2]))
  return(extracted_text)
}


# Applying the function to the input vector
ec_odisha_main$submit <- extract_after_colon(ec_odisha_main$Date_1) %>% dmy()
ec_odisha_main$grant <- extract_after_colon(ec_odisha_main$Date_2) %>% dmy()

#Time taken to Grant 
ec_odisha_main$time <- as.duration(ec_odisha_main$grant - ec_odisha_main$submit)/ddays(1)



```


-------------------------------------------------------


```{r}
summary(ec_odisha_main$time)
```


```{r extract-year}
#Year of Submission
ec_odisha_main$submit_year<-(gsub('^([0-9][0-9][0-9][0-9]).*','\\1',ec_odisha_main$submit))
ec_odisha_main$submit_year <- year(ec_odisha_main$submit)

#Year-Month of Submission
ec_odisha_main$submit_year_mon<-as.yearmon(ec_odisha_main$submit)

ec_odisha_main_summary<-ec_odisha_main%>%
  group_by(Category_Simplified,Status_Simplified,submit_year_mon,submit_year)%>%
  summarise(n=n())

ggplot(filter(ec_odisha_main_summary,Category_Simplified=='Non-Coal Mining'), aes(x = submit_year_mon, y = n)) +
  geom_point(fill = "skyblue", width = 0.5)  +
  labs(title = "Summary Of Application Type",
       x = "Time",
       y = "N") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Tilting x-axis labels by 45 degrees
facet_wrap(~Status_Simplified)
```


```{r}
density_year_mining <- ggplot(filter(ec_odisha_main_summary,Category_Simplified=='Non-Coal Mining'), aes(x = submit_year)) +
  geom_bar() +
  theme_minimal() + facet_wrap(~Category_Simplified) + ggtitle('EC Granted (Non-Coal Mining)')

print(density_year_mining)+facet_wrap(~Status_Simplified)


density_year_infra <- ggplot(filter(ec_odisha_main_summary,Category_Simplified=='INFRA'), aes(x = submit_year)) +
  geom_bar() +
  theme_minimal() + facet_wrap(~Category_Simplified) + ggtitle('EC Granted (INFRA)')

print(density_year_infra)+facet_wrap(~Status_Simplified)

density_year_industrial <- ggplot(filter(ec_odisha_main_summary,Category_Simplified=='Industrial'), aes(x = submit_year)) +
  geom_bar() +
  theme_minimal() + facet_wrap(~Category_Simplified) + ggtitle('EC Granted (Industrial)')

print(density_year_industrial)+facet_wrap(~Status_Simplified)
```





-------------------------------------------------






## Limit to EC Granted 

```{r}
grant_ec <- ec_odisha_main %>% filter(Status %in% c("EC Granted","EC Granted - Processed offline")) %>% distinct()

```

## Look for Duplicates

```{r}
grant_ec$duplicate <- duplicated(grant_ec$Proposal)
table(grant_ec$duplicate)
```

## How many location identifiers are missing? 

```{r}
grant_ec%>%
  group_by(District)%>%
  count()%>%
  arrange(-n)%>%
  ungroup()%>%
  mutate(Percent=round(n*100/sum(n),0))
```

##Simplify the Categories of Projects 

- 68% are non-coal mining projects 

```{r}

grant_ec%>%
  group_by(Category_Simplified)%>%
  count()%>%
  arrange(-n)%>%
  ungroup()%>%
  mutate(Percent=round(n*100/sum(n),0))

```



```{r}
summary(grant_ec$time)

#Exclude if length  less than 0

grant_ec <- grant_ec %>% filter(time >=0) #Some obs have negative grant time

grant_ec_summary<-grant_ec%>%
  filter(!is.na(time))%>%
  group_by(Category_Simplified)%>%
  summarise(mean=mean(time),
            sd=sd(time))

ggplot(grant_ec_summary, aes(x = Category_Simplified, y = mean)) +
  geom_point(fill = "skyblue", width = 0.5) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.2, color = "black", size = 0.7) +
  geom_text(aes(label = round(mean, 2)), vjust = -0.5, size = 3) +
  labs(title = "Summary Of Processing Time (EC Granted)",
       x = "Project Category",
       y = "Mean") +
  theme_minimal()
```


```{r extract-year}
#Year of Submission
grant_ec$submit_year<-(gsub('^([0-9][0-9][0-9][0-9]).*','\\1',grant_ec$submit))
grant_ec$submit_year <- year(grant_ec$submit)

#Year-Month of Submission
grant_ec$submit_year_mon<-as.yearmon(grant_ec$submit)

grant_ec_summary<-grant_ec%>%
  filter(!is.na(time))%>%
  group_by(Category_Simplified,submit_year)%>%
  summarise(mean=mean(time),
            sd=sd(time),
            n=n())

ggplot(filter(grant_ec_summary,Category_Simplified!='Other'), aes(x = submit_year, y = mean)) +
  geom_point(fill = "skyblue", width = 0.5) +
  geom_errorbar(aes(ymin = mean - sd, ymax = mean + sd), width = 0.2, color = "black", size = 0.7) +
  geom_text(aes(label = round(mean, 2)), vjust = -0.5, size = 3) +
  labs(title = "Summary Of Processing Time (EC Granted)",
       x = "Project Category",
       y = "Mean") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Tilting x-axis labels by 45 degrees
facet_wrap(~Category_Simplified)
```


```{r}
density_year <- ggplot(grant_ec, aes(x = submit_year)) +
  geom_bar() +
  theme_minimal() + facet_wrap(~Category_Simplified) + ggtitle('EC Granted')

print(density_year)
```


## Descriptives







```{r}
density_year_infra_orissa <- ggplot(filter(grant_ec,State=='Orissa'), aes(x = submit_year_mon, y = time)) +geom_vline(xintercept = as.yearmon('May 2019'), linetype="dashed", 
             color = "black", size=1)+
  geom_point(fill = "skyblue", color = "darkblue", alpha = 0.5) + scale_x_yearmon()+
  theme_minimal() + ggtitle('Odisha Projects Around Elections (EC)')  +facet_wrap(~Category_Simplified)

print(density_year_infra_orissa)
```






```{r}
ggplot(grant_ec, aes(x = Category)) +
  geom_bar(aes(y = (..count..)/sum(..count..)), fill = "skyblue", color = "darkblue") +
  labs(x = "Category", y = "Percentage", title = "Category - EC granted") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```

```{r}
ggplot(grant_ec, aes(x = Category, y = time)) +
  geom_boxplot(fill = "skyblue", color = "darkblue", outlier.shape = NA) +
  labs(x = "Group", y = "Value", title = "Box Plot") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))
```





##Look at Political Alignment 

```{r}
alignment <- read.csv(paste0("C:/Users/",user,"/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Odisha_Tehsil_AC_Aligned.csv"),
                             stringsAsFactors = F)


library(tidyverse)
library(stringdist)


# Define a function for fuzzy matching
fuzzy_match <- function(string1, string2) {
  # Calculate the Jaro-Winkler distance between two strings
  dist <- stringdist::stringdist(string1, string2, method = "lcs")
  # Return TRUE if the distance is below a certain threshold, indicating a match
  return(min(dist))  # Adjust the threshold as needed
}

ec_odisha_main_filter_tehsil<-ec_odisha_main%>%
  filter(Tehsil!='')
ec_odisha_main_filter_tehsil$District_Tehsil<-tolower(trimws(paste(ec_odisha_main_filter_tehsil$District,ec_odisha_main_filter_tehsil$Tehsil,sep=' ')))
alignment$District_Tehsil<-tolower(trimws(paste(alignment$Dist_Nam_1,alignment$Tehsil,sep=' ')))


temp<-fuzzy_match(ec_odisha_main_filter_tehsil$District_Tehsil[1],alignment$District_Tehsil)

ec_odisha_main_filter_tehsil$District_Tehsil[1]

# Use rowwise() and mutate() to apply the fuzzy_match function row-wise
matrix_matches<-stringdist::stringdistmatrix(ec_odisha_main_filter_tehsil$District_Tehsil,
                                                              alignment$District_Tehsil,method='lcs')

min_value_matrix_matches<-apply(matrix_matches,1,min)
table(min_value_matrix_matches)

min_index_list<-apply(matrix_matches,1,which.min)

ec_odisha_main_filter_tehsil$TUID<-NA
ec_odisha_main_filter_tehsil$District_matched<-NA
ec_odisha_main_filter_tehsil$Tehsil_matched<-NA
ec_odisha_main_filter_tehsil$Matched_distance<-NA

ec_odisha_main_filter_tehsil$District_matched=
  sapply(1:length(min_index_list), 
         function(x){alignment$Dist_Nam_1[min_index_list[x]]})

ec_odisha_main_filter_tehsil$Tehsil_matched=
  sapply(1:length(min_index_list), 
         function(x){alignment$Tehsil[min_index_list[x]]})

ec_odisha_main_filter_tehsil$tuid=
  sapply(1:length(min_index_list), 
         function(x){alignment$tuid[min_index_list[x]]})


ec_odisha_main_filter_tehsil$Matched_distance=
  sapply(1:length(min_index_list), function(x){min_value_matrix_matches[x]})



```


##Merge at Tehsil Level 



```{r}

library(lfe)

ec_odisha_main_filter_tehsil <- left_join(ec_odisha_main_filter_tehsil,alignment,by="tuid")

ec_odisha_main_filter_tehsil$Deslisted<-ifelse(ec_odisha_main_filter_tehsil$Status_Simplified=='Delisted',1,0)
ec_odisha_main_filter_tehsil$Rejected<-ifelse(ec_odisha_main_filter_tehsil$Status_Simplified=='Rejected',1,0)
ec_odisha_main_filter_tehsil$Withdrawn<-ifelse(ec_odisha_main_filter_tehsil$Status_Simplified=='Withdrawn',1,0)


table(ec_odisha_main_filter_tehsil$Deslisted)



summary(felm(Deslisted~Per_Pop_Aligned|Category_Simplified|0|0,data=filter(ec_odisha_main_filter_tehsil,Matched_distance<5)))


summary(felm(Deslisted~Per_Pop_Aligned|Category_Simplified+submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil,Matched_distance<5)))

summary(felm(Deslisted~Per_Pop_Aligned|submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil,grepl('TAHASILDAR',ec_odisha_main_filter_tehsil$Company)&Matched_distance<5)))

ec_odisha_main_filter_tehsil_mining<-filter(ec_odisha_main_filter_tehsil,Category_Simplified=='Non-Coal Mining')


summary(felm(Deslisted~Per_Pop_Aligned|submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil_mining,Status_Simplified!='Other')))

summary(felm(Deslisted~Per_Pop_Aligned|0|0|0,data=filter(ec_odisha_main_filter_tehsil_mining,submit_year>2019)))


ec_odisha_main_filter_tehsil_mining$Tehsildar<-ifelse(grepl('TAHASILDAR',ec_odisha_main_filter_tehsil_mining$Company),1,0)

ec_odisha_main_filter_tehsil_mining$Sand<-ifelse(grepl('sand',tolower(ec_odisha_main_filter_tehsil_mining$Proposal.Name)),1,0)

table(ec_odisha_main_filter_tehsil_mining$Sand)
table(ec_odisha_main_filter_tehsil_mining$Tehsildar)



summary(felm(Deslisted~Per_Pop_Aligned|0|0|0,data=filter(ec_odisha_main_filter_tehsil_mining,Status_Simplified!='Other')))



summary(felm(Deslisted~Sand|0|0|tuid,data=filter(ec_odisha_main_filter_tehsil_mining,Status_Simplified!='Other'&submit_year<2019)))


summary(felm(Deslisted~Tehsildar|submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil_mining)))
```

##Merge at Tehsil Level 



```{r}

grant_ec_filter_tehsil<-ec_odisha_main_filter_tehsil%>%
  filter(Status %in% c("EC Granted","EC Granted - Processed offline")) %>% distinct()
```


## Detailed Timing 

```{r}

##Merge Detailed Timeline Dataset with EC Granted dataset 
table(grant_ec_filter_tehsil$Proposal%in%ec_detailed_timeline_odisha$Proposal.Number)
grant_ec_filter_tehsil$Proposal.Number<-grant_ec_filter_tehsil$Proposal

table(duplicated(paste(ec_detailed_timeline_odisha$Proposal.Number,ec_detailed_timeline_odisha$Project.Name)))


grant_ec_filter_tehsil<-dplyr::left_join(grant_ec_filter_tehsil,ec_detailed_timeline_odisha,by='Proposal.Number')


##Create Variables that Divide the Overall time for process EC
##into the following components

# Applying the function to the input vector

#Time taken between SEIAA and SEAC

grant_ec_filter_tehsil$Accepted.by.SEIAA.and.forwarded.to.SEAC <- grant_ec_filter_tehsil$Accepted.by.SEIAA.and.forwarded.to.SEAC %>% dmy()

grant_ec_filter_tehsil$Accepted.by.SEAC <- grant_ec_filter_tehsil$Accepted.by.SEAC %>% dmy()

#Time taken to Grant 
grant_ec_filter_tehsil$time_SEIAA_SEAC <- as.duration(grant_ec_filter_tehsil$Accepted.by.SEAC - grant_ec_filter_tehsil$Accepted.by.SEIAA.and.forwarded.to.SEAC)/ddays(1)

summary(grant_ec_filter_tehsil$time_SEIAA_SEAC)

#Time taken to Grant 
grant_ec_filter_tehsil$EC_Letter_Uploaded <- grant_ec_filter_tehsil$EC.Letter.Uploaded.On.EC.Granted %>% dmy()


grant_ec_filter_tehsil$time_submit_seiaa<-as.duration(grant_ec_filter_tehsil$Accepted.by.SEIAA.and.forwarded.to.SEAC - grant_ec_filter_tehsil$submit)/ddays(1)

grant_ec_filter_tehsil$time_SEAC_Grant <- as.duration(grant_ec_filter_tehsil$grant - grant_ec_filter_tehsil$Accepted.by.SEAC)/ddays(1)

summary(grant_ec_filter_tehsil$time)
summary(grant_ec_filter_tehsil$time_submit_seiaa)
which(grant_ec_filter_tehsil$time_submit_seiaa<0)

summary(grant_ec_filter_tehsil$time_SEIAA_SEAC)

which(grant_ec_filter_tehsil$time_SEIAA_SEAC<0)

summary(grant_ec_filter_tehsil$time_SEAC_Grant)

which(grant_ec_filter_tehsil$time_SEAC_Grant<0)



```




```{r plots}
ggplot(filter(grant_ec_filter_tehsil,time_SEIAA_SEAC>0&time>0), aes(x = time_SEIAA_SEAC, y = time)) +
  geom_point(fill = "skyblue", width = 0.5) +
  labs(title = "Summary Of Processing Time (EC Granted)",
       x = "Time Taken between SEIAA and SEAC to Approve",
       y = "Overall Time") +
  theme_minimal()

grant_ec_filter_tehsil$time_seac_percent<-grant_ec_filter_tehsil$time_SEIAA_SEAC/grant_ec_filter_tehsil$time

summary(grant_ec_filter_tehsil$time_seac_percent)

ggplot(filter(grant_ec_filter_tehsil,time_seac_percent<1&time>0), aes(time_seac_percent)) +
  geom_histogram() +
  labs(title = "Summary Of Processing Time (EC Granted)",
       x = "Time Taken by SEAC to Approve",
       y = "Count") +
  theme_minimal()

ggplot(filter(grant_ec_filter_tehsil,time_seac_percent<1&time>0), aes(x = Category_Simplified, y = time_seac_percent)) +
  geom_boxplot(fill = "skyblue", color = "darkblue", outlier.shape = NA) +
  labs(x = "Group", y = "Time Taken by SEAC as Percentage", title = "Box Plot") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

ggplot(filter(grant_ec_filter_tehsil,time_submit_seiaa>0&time>0), aes(x = time_submit_seiaa, y = time)) +
  geom_point(fill = "skyblue", width = 0.5) +
  labs(title = "Summary Of Processing Time (EC Granted)",
       x = "Time Taken by seiaa to Approve",
       y = "Overall Time") +
  theme_minimal()

```





```{r}
density_year_infra_orissa <- ggplot(filter(grant_ec_filter_tehsil,time_seac_percent<1), aes(x = submit_year_mon, y = time_seac_percent)) +geom_vline(xintercept = as.yearmon('May 2019'), linetype="dashed", 
             color = "black", size=1)+
  geom_point(fill = "skyblue", color = "darkblue", alpha = 0.5) + scale_x_yearmon()+
  theme_minimal() + ggtitle('Odisha Projects Around Elections (EC)')  +facet_wrap(~Category_Simplified)

print(density_year_infra_orissa)


```


```{r}


grant_ec_filter_tehsil_non_coal<-grant_ec_filter_tehsil%>%
  filter(Category_Simplified=='Non-Coal Mining')

grant_ec_filter_tehsil_non_coal$Tehsildar<-ifelse(grepl('TAHASILDAR',grant_ec_filter_tehsil_non_coal$Company),1,0)

table(grant_ec_filter_tehsil_non_coal$Tehsildar)


density_year_infra_orissa <- ggplot(filter(grant_ec_filter_tehsil_non_coal,time>0&submit_year>2019), aes(x = submit_year_mon, y = time)) +geom_vline(xintercept = as.yearmon('May 2019'), linetype="dashed", 
             color = "black", size=1)+
  geom_point(fill = "skyblue", color = "darkblue", alpha = 0.5) + scale_x_yearmon()+
  theme_minimal() + ggtitle('Odisha Projects Around Elections (EC)')+
theme(axis.text.x = element_text(angle = 45, hjust = 1)) + # Tilting x-axis labels by 45 degrees
facet_wrap(~Tehsildar)

print(density_year_infra_orissa)

grant_ec_filter_tehsil_non_coal$Tehsildar_Factor=as.factor(grant_ec_filter_tehsil_non_coal$Tehsildar)

ggplot(filter(grant_ec_filter_tehsil_non_coal,time>0&submit_year>2019), aes(x=time, fill=Tehsildar_Factor)) +
  geom_density(alpha=0.24) + # alpha for transparency to see overlap
  labs(title="Non Coal Mining Post 2019",
       x="Value",
       y="Density") +
  theme_minimal() # Using a minimal theme for aesthetics
```

#Analysis All Categories

```{r analysis}
library(lfe)

summary(felm(time~Per_Pop_Aligned|0|0|0,data=grant_ec_filter_tehsil))

summary(felm(time~Per_Pop_Aligned|Category_Simplified|0|0,data=grant_ec_filter_tehsil))

summary(felm(time~Per_Pop_Aligned|Category_Simplified|0|tuid,data=grant_ec_filter_tehsil))

summary(felm(time~Per_Pop_Aligned|Category_Simplified+submit_year|0|0,data=grant_ec_filter_tehsil))

summary(felm(time~Per_Pop_Aligned|Category_Simplified+submit_year|0|tuid,data=grant_ec_filter_tehsil))

summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|Category_Simplified+submit_year|0|tuid,data=grant_ec_filter_tehsil))

summary(felm(time_SEAC_Grant~Per_Pop_Aligned|Category_Simplified+submit_year|0|tuid,data=grant_ec_filter_tehsil))

```



```{r mining}
summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|submit_year|0|0,data=filter(grant_ec_filter_tehsil,grepl('TAHASILDAR',grant_ec_filter_tehsil$Company))))

grant_ec_filter_tehsil_mining<-filter(grant_ec_filter_tehsil,Category_Simplified=='Non-Coal Mining')


summary(felm(time_SEAC_Grant~Per_Pop_Aligned|submit_year|0|0,data=filter(grant_ec_filter_tehsil_mining,!grepl('TAHASILDAR',grant_ec_filter_tehsil_mining$Company))))

summary(felm(time_submit_seiaa~Per_Pop_Aligned|submit_year|0|0,data=filter(grant_ec_filter_tehsil_mining)))

summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|submit_year|0|0,data=filter(grant_ec_filter_tehsil_mining)))

summary(felm(time_SEAC_Grant~Per_Pop_Aligned|submit_year|0|0,data=filter(grant_ec_filter_tehsil_mining)))

summary(felm(time~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining)))

```





```{r post-election}

summary(felm(time~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year>2019)))

summary(felm(time_submit_seiaa~Per_Pop_Aligned|0|0|tuid,data=filter(grant_ec_filter_tehsil_mining,submit_year>2019)))

summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year>2019)))

summary(felm(time_SEAC_Grant~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year>2019)))


```


```{r robust}
summary(felm(time~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year<2020)))

summary(felm(time_submit_seiaa~Per_Pop_Aligned|0|0|tuid,data=filter(grant_ec_filter_tehsil_mining,submit_year<2020)))

summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year<2020)))

summary(felm(time_SEAC_Grant~Per_Pop_Aligned|0|0|tuid,data=filter(grant_ec_filter_tehsil_mining,submit_year<2020)))

```




```{r sand}
grant_ec_filter_tehsil_mining$Tehsildar<-ifelse(grepl('TAHASILDAR',grant_ec_filter_tehsil_mining$Company),1,0)

table(grant_ec_filter_tehsil_mining$Tehsildar)
round(prop.table(xtabs(~grant_ec_filter_tehsil_mining$Tehsildar+grant_ec_filter_tehsil_mining$submit_year),2),2)



grant_ec_filter_tehsil_mining$Sand<-ifelse(grepl('sand',tolower(grant_ec_filter_tehsil_mining$Proposal.Name)),1,0)

table(grant_ec_filter_tehsil_mining$Sand)
round(prop.table(xtabs(~grant_ec_filter_tehsil_mining$Sand+grant_ec_filter_tehsil_mining$submit_year),2),2)


summary(felm(time~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,Sand==1)))

summary(felm(time~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,Sand==1&time>0)))

summary(felm(time_SEIAA_SEAC~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,Tehsildar==0)))

summary(felm(time_SEAC_Grant~Per_Pop_Aligned|0|0|0,data=filter(grant_ec_filter_tehsil_mining,time_SEAC_Grant>0&submit_year>2020)))

summary(felm(log(1+time_SEIAA_SEAC)~Per_Area_Aligned+Tehsildar|0|0|0,data=filter(grant_ec_filter_tehsil_mining,submit_year>2020&Sand==1)))

summary(felm(time_SEIAA_SEAC~Sand+Tehsildar+Per_Pop_Aligned|submit_year|0|tuid,data=filter(grant_ec_filter_tehsil_mining,time_SEAC_Grant>0)))



summary(felm(time_SEAC_Grant~Sand|submit_year|0|tuid,data=filter(grant_ec_filter_tehsil_mining,time_SEAC_Grant>0)))



```

```{r}
density_year_infra_orissa <- ggplot(filter(grant_ec_filter_tehsil_mining,Sand==1), aes(x = submit_year_mon, y = time)) +geom_vline(xintercept = as.yearmon('May 2019'), linetype="dashed", 
             color = "black", size=1)+
  geom_point(fill = "skyblue", color = "darkblue", alpha = 0.5) + scale_x_yearmon()+
  theme_minimal() + ggtitle('Odisha Sand Mining Projects Around Elections (EC)')+facet_wrap(~Tehsildar)

print(density_year_infra_orissa)
```



#Location of Firm/Applicant and Processing Time

- Are firms located closer to the city of Bhubaneswar more likely to get faster approval?
- Insider Outsider? 
- Only for Form 2 1138 projects get lat long for project firm location
- Then use distance to calculate distance from Bhubaneswar? 
- Also distance from Project 
- run regression to see if distance predicts anything 

```{r ggmap-zip}
install.packages("ggmap")
library(ggmap)
register_google

register_google(key = "AIzaSyBUOxkob_AsOFbmLRpfE2fE2sqzpnpHElY")

# Example Indian zip code
indian_zip_code <- "761107"

# Geocode the zip code
location <- geocode(indian_zip_code)

# Print latitude and longitude
print(location$lon)
print(location$lat)


ec_form2_odisha_pincode<-ec_form2_odisha%>%
  dplyr::filter(!is.na(Pincode))

ec_form2_odisha_pincode$firm_lon<-NA
 ec_form2_odisha_pincode$firm_lat<-NA

 for(i in 1:nrow(ec_form2_odisha_pincode)){
  print(i)
  location <- geocode(as.character(ec_form2_odisha_pincode$Pincode[i]))
 ec_form2_odisha_pincode$firm_lon[i]=location$lon
 ec_form2_odisha_pincode$firm_lat[i]=location$lat
}

write.csv(ec_form2_odisha_pincode,'C:/Users/agnihotri/Dropbox/agnihotri_gupta/Environment_Clearance/Orissa/Backups/ec_form2_odisha_pincode.csv')

```

#distance from capital city

```{r distance}
library(geosphere)
library(dplyr)



get_geo_distance = function(long1, lat1, long2, lat2, units = "miles") {
  
  distance_m = distm(c(long1, lat1), c(long2, lat2), fun = distHaversine)
  if (units == "km") {
    distance = distance_m / 1000.0;
  }
  else if (units == "miles") {
    distance = distance_m / 1609.344
  }
  else {
    distance = distance_m
    # This will return in meter as same way as distHaversine function. 
  }
  distance
}
#bhubaneswar
#
ec_form2_odisha_pincode$lat_bbsr<-20.261599
ec_form2_odisha_pincode$lon_bbsr<-85.836685
distm(c(lon1, lat1), c(lon2, lat2), fun = distHaversine)


get_geo_distance(ec_form2_odisha_pincode$firm_lon[1],ec_form2_odisha_pincode$firm_lat[1],ec_form2_odisha_pincode$lon_bbsr[1],ec_form2_odisha_pincode$lat_bbsr[1],units='km')

ec_form2_odisha_pincode<-ec_form2_odisha_pincode %>% 
  dplyr::rowwise() %>% 
  dplyr::mutate(dist_from_bbsr= get_geo_distance(firm_lon,firm_lat,lon_bbsr,lat_bbsr,units='km'))

summary(ec_form2_odisha_pincode$dist_from_bbsr)



```

```{r analysis}

#Delisted
ec_form2_odisha_pincode_select<-ec_form2_odisha_pincode%>%
  select(Proposal,dist_from_bbsr)

library(lfe)

ec_odisha_main_filter_tehsil_pincode <- left_join(ec_odisha_main_filter_tehsil,ec_form2_odisha_pincode_select,by="Proposal")


table(ec_odisha_main_filter_tehsil_pincode$Deslisted)
table(is.na(ec_odisha_main_filter_tehsil_pincode$dist_from_bbsr))




summary(felm(Deslisted~dist_from_bbsr|0|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode,Matched_distance<5)))


summary(felm(Deslisted~dist_from_bbsr|Category_Simplified+submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode,Matched_distance<5)))


ec_odisha_main_filter_tehsil_pincode_mining_pincode<-filter(ec_odisha_main_filter_tehsil_pincode,Category_Simplified=='Non-Coal Mining')


summary(felm(Deslisted~dist_from_bbsr|submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode_mining_pincode_pincode,Status_Simplified!='Other')))

summary(felm(Deslisted~dist_from_bbsr|0|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode_mining_pincode,submit_year>2019)))


ec_odisha_main_filter_tehsil_pincode_mining_pincode$Tehsildar<-ifelse(grepl('TAHASILDAR',ec_odisha_main_filter_tehsil_pincode_mining_pincode$Company),1,0)

ec_odisha_main_filter_tehsil_pincode_mining_pincode$Sand<-ifelse(grepl('sand',tolower(ec_odisha_main_filter_tehsil_pincode_mining_pincode$Proposal.Name)),1,0)

table(ec_odisha_main_filter_tehsil_pincode_mining_pincode$Sand)
table(ec_odisha_main_filter_tehsil_pincode_mining_pincode$Tehsildar)



summary(felm(Deslisted~dist_from_bbsr|0|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode_mining_pincode,Status_Simplified!='Other')))





summary(felm(Deslisted~dist_from_bbsr|submit_year|0|0,data=filter(ec_odisha_main_filter_tehsil_pincode_mining_pincode)))
```
#Analysis All Categories

```{r analysis}
library(lfe)
ec_form2_odisha_pincode_select<-ungroup(ec_form2_odisha_pincode_select)
table(ec_form2_odisha_pincode_select$Proposal%in%grant_ec_filter_tehsil$Proposal)

temp<-inner_join(grant_ec_filter_tehsil,ec_form2_odisha_pincode_select,by="Proposal")

temp<-temp%>%
  filter(!duplicated(Proposal))
temp$distance<-temp$dist_from_bbsr

summary(felm(time~dist_from_bbsr|0|0|0,data=temp))

summary(felm(time~dist_from_bbsr|Category_Simplified|0|0,data=temp))

summary(felm(time~dist_from_bbsr|Category_Simplified|0|tuid,data=temp))

summary(felm(time~dist_from_bbsr|Category_Simplified+submit_year|0|0,data=temp))

summary(felm(time~dist_from_bbsr|Category_Simplified+submit_year|0|tuid,data=temp))

summary(felm(time_SEIAA_SEAC~dist_from_bbsr|Category_Simplified+submit_year|0|tuid,data=temp))

summary(felm(time_SEAC_Grant~dist_from_bbsr|Category_Simplified+submit_year|0|tuid,data=temp))

```


## Maps Odisha

```{r}
time_or <- ggplot(shp_or)+
geom_sf(aes(fill = avg)) +
## custom gradient 
scale_fill_gradientn(colors = rcartocolor::carto_pal(name = "BluYl", n =7),limits=c(60,250))+## clean map theme from cowplot
theme_map()+
labs(title = "Avg Time - Odisha", fill = "Days")+ theme(plot.title = element_text(hjust = .5))

print(time_or)
```

```{r}
count_or <- ggplot(shp_or)+
geom_sf(aes(fill = count)) +
## custom gradient 
scale_fill_gradientn(colors = rcartocolor::carto_pal(name = "BluYl", n =7),limits=c(0,200))+## clean map theme from cowplot
theme_map()+
labs(title = "No. of Projects - Odisha", fill = "Count")+ theme(plot.title = element_text(hjust = .5))

print(count_or)
```


```{r}
cd_or <- ggplot(shp_or)+
geom_sf(aes(fill = cd)) +
## custom gradient 
scale_fill_gradientn(colors = rcartocolor::carto_pal(name = "BluYl", n =7),limits=c(0,1.5))+## clean map theme from cowplot
theme_map()+
labs(title = "Coeff. of Dev. - Odisha", fill = "CD")+ theme(plot.title = element_text(hjust = .5))

print(cd_or)
```

```{r}
most_or <- ggplot(shp_or)+
geom_sf(aes(fill = most)) +
## custom gradient 
scale_fill_manual(values = c("red", "blue", "green", "orange","skyblue"), na.value = "grey") +## clean map theme from cowplot
theme_map()+
labs(title = "Categories - Odisha", fill = "CD")+ theme(plot.title = element_text(hjust = .5))

print(most_or)
```

## Maps - Haryana

```{r}
time_har <- ggplot(shp_har)+
geom_sf(aes(fill = avg)) +
## custom gradient 
scale_fill_gradientn(colors = rcartocolor::carto_pal(name = "BluYl", n =7),limits=c(80,999))+## clean map theme from cowplot
theme_map()+
labs(title = "Avg Time - Haryana", fill = "Days")+ theme(plot.title = element_text(hjust = .5))

print(time_har)
```

```{r}
count_har <- ggplot(shp_har)+
geom_sf(aes(fill = count)) +
## custom gradient 
scale_fill_gradientn(colors = rcartocolor::carto_pal(name = "BluYl", n =7),limits=c(1,270))+## clean map theme from cowplot
theme_map()+
labs(title = "No. of Projects - Haryana", fill = "Count")+ theme(plot.title = element_text(hjust = .5))

print(count_har)
```











